Prediction of the 2020 Presidential Election

### 2020-11-01 outputs/paper/paper.Rmd
F

---
title: "Prediction of the 2020 Presidential Election"
subtitle: "Spoiler Alert: Biden Wins"
author: "Anees Shaikh, Jaffa Romain, Lu Mu, and Cameron Fryer"
thanks: "Code and data are available at: https://github.com/aneesshake/elections_prediction"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: |
  | In this paper, we first consider the Democracy Fund + UCLA Nationscape Wave 50 dataset, which contains the results of a survey (conducted June 25-July 1, 2020) on American voter attitudes. Thereafter, the survey data is used to train a model relating voter intent to a few explanatory variables. The model is then applied to the post-stratification dataset; namely, the results of the 2018 1-year American Community Survey (ACS). Since the ACS data pertains to individual persons and their characteristics, the associated use of our model allows us to conclude that Joe Biden will be the next President of the United States.
  |
  | **Keywords:** forecasting; US 2020 election; Trump; Biden; multilevel regression with post-stratification
output:
  bookdown::pdf_document2:
    citation_package: natbib
toc: FALSE
bibliography: references.bib
---

@@

library(tidyverse)
library(tinytex)
```

@@

Our model uses the variables pertaining to age, state, race, sex, household income, and whether a voter is Hispanic to predict our dependent variable. 
The model takes the form:
***  TO DO: Regression and Other Stories to cite equation **
$$ Pr(y_i = 1) = logit^-1(X_i *\beta) $$
where $y_i$ = 1 represents a voter voting for Trump in the election.
$ Pr(y_i = 1) $ is the probability of a voter choosing to vote for Trump.
The $ X_i\beta $ are the linear predictors, where $\beta$ represents the fitted coefficients for each independent variable $ X_i $ in the model.

The logit function $logit(x) = log(x/1-x)$ maps the range (0, 1) to $(-\infinity, \infinity)$.
Its inverse function $ logit^-1(x) = e^x/(1+e^x)$ maps back to the unit range. 
The model's output is bounded between 0 and 1, unlike a linear regression model, mapping the outputs into a binary outcome, and says that the probability that some person $i$, will vote for Trump depends on their age, sex, state, household income,and whether the voter is Hispanic.

We are running our regresion model using the 'glm()' function in [R]. The fitted model results in the following coefficients:
```{r}

>>>>

---
title: "Prediction of the 2020 Presidential Election"
subtitle: "Spoiler Alert: Biden Wins"
author: "Anees Shaikh, Jaffa Romain, Lu Mu, and Cameron Fryer"
thanks: "Code and data are available at: https://github.com/aneesshake/elections_prediction"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: |
  | The purpose of this analysis is to forecast the results of the upcoming United States 2020 presidential election. In this paper, we first consider the Democracy Fund + UCLA Nationscape Wave 50 dataset, which contains the results of a survey (conducted June 25-July 1, 2020) on American voter attitudes. Thereafter, the survey data is used to train a model relating voter intent to a few explanatory variables. The model is then applied to the post-stratification dataset; namely, the results of the 2018 1-year American Community Survey (ACS). Since the ACS data pertains to individual persons and their characteristics, the associated use of our model allows us to conclude that Joe Biden will be the next President of the United States.|
Keywords: forecasting; US 2020 election; Trump; Biden; multilevel regression with post-stratification
output:
  bookdown::pdf_document2:
    citation_package: natbib
toc: FALSE
bibliography: references.bib
---

@@

library(tidyverse)
library(tinytex)
library(readr)
```

@@

Our model uses the variables pertaining to age, state, race, sex, household income, and whether a voter is Hispanic to predict whether a respondent will vote for Trump or Biden in the elections. 
The model takes the form:
***  TO DO: Regression and Other Stories to cite equation **
$$ Pr(y_i = 1) = logit^-1(X_i *\beta) $$

where $y_i = 1$ represents a voter voting for Trump in the election.
$Pr(y_i = 1)$ is the probability of a voter choosing to vote for Trump.
The $X_i\beta$ are the linear predictors, where $\beta$ represents the fitted coefficients for each independent variable $X_i$ in the model. The coefficient values signify the mean variable changes in a one unit shift in the given variable $\beta$.
The logit function $logit(x) = log(x/1-x)$ maps the range (0, 1) to $(-\infty, \infty)$.
Its inverse function $logit^-1(x) = e^x/(1+e^x)$ maps back to the unit range. 
The model's output is bounded between 0 and 1,  mapping the outputs into a binary outcome. The output tells us the probability that some person $i$, will vote for Trump depends on their age, sex, state, household income, and whether the voter is Hispanic.

We are running our regression model using the 'glm()' function in [R]. The fitted model results in the following coefficients:
```{r}
```
